HTGT Migration

HTGT currently runs on an old version of Linux (etch or lenny). In order to provide resilience and the ability to support
over an extended timelscale, we need to have HTGT run on a more recent version of Ubuntu, which is precise (v12.04).

Bringing up the HTGT system in a development environment.


Start with HTGT-db

Contents of /etc/lsb-release:

dp10@htgt3:~/svn-checkout/htgt-webapp-trunk[Devel]$ more /etc/lsb-release 
DISTRIB_ID=Ubuntu
DISTRIB_RELEASE=12.04
DISTRIB_CODENAME=precise
DISTRIB_DESCRIPTION="Ubuntu 12.04.2 LTS"


Current Perl and htgt related environment:

dp10@htgt3:~[Devel]$ which perl
/software/perl-5.8.9/bin/perl
dp10@htgt3:~[Devel]$ set | grep -i htgt
HOSTNAME=htgt3
HTGT_CACHE_ROOT=/var/tmp/htgt-cache.dp10
HTGT_DB=eucomm_vector_esmt
HTGT_DBCONNECT=/software/team87/brave_new_world/conf/dbconnect.cfg
HTGT_ENSEMBL_HOST=ensembldb.ensembl.org
HTGT_ENSEMBL_USER=anonymous
HTGT_ENV=Devel
HTGT_QC_CONF=/software/team87/brave_new_world/conf/qc.conf
HTGT_QC_DIST_LOGIC_CONF=/software/team87/brave_new_world/conf/qc-dist-logic.conf
HTGT_SUBMITQC_FORCE_RUN=
PS1='\u@\h:\w[$HTGT_ENV]\$ '
    htgt-build.pl build "$@"
htgt-install () 
        echo 'Usage: htgt-install MODULE-VERSION.tar.gz' 1>&2;
    svn ls "svn+ssh://svn.internal.sanger.ac.uk/repos/svn/htgt/projects/$1/branches"
    svn ls "svn+ssh://svn.internal.sanger.ac.uk/repos/svn/htgt/projects"
    svn ls "svn+ssh://svn.internal.sanger.ac.uk/repos/svn/htgt/projects/$1/tags"
    svn cp "svn+ssh://svn.internal.sanger.ac.uk/repos/svn/htgt/projects/${project}/trunk" "svn+ssh://svn.internal.sanger.ac.uk/repos/svn/htgt/projects/${project}/branches/${branch}" "$@"
    exec htgt-env.pl --$1
    htgt-build.pl tag "$@"

INSTALL local::lib

Copy the tar and follow the instructions to install in the usual place.

export PERL_LOCAL_LIB_ROOT="$PERL_LOCAL_LIB_ROOT:/nfs/users/nfs_d/dp10/work/htgt_migration/htgt_perl5";
export PERL_MB_OPT="--install_base /nfs/users/nfs_d/dp10/work/htgt_migration/htgt_perl5";
export PERL_MM_OPT="INSTALL_BASE=/nfs/users/nfs_d/dp10/work/htgt_migration/htgt_perl5";
export PERL5LIB="/nfs/users/nfs_d/dp10/work/htgt_migration/htgt_perl5/lib/perl5:$PERL5LIB";
export PATH="/nfs/users/nfs_d/dp10/work/htgt_migration/htgt_perl5/bin:$PATH";

PATH Specification

/nfs/users/nfs_d/dp10/work/htgt_migration/htgt_perl5/bin:/bin:/usr/bin

PERL5LIB Specification

/nfs/users/nfs_d/dp10/work/htgt_migration/htgt_perl5/lib/perl5:

Checkpoint: 16 July 2013

module: htgtdb-trunk

10-htgt-utils-pass-level.t  All tests complete 
30-design.t - cannot load the dbfactory so need to skip to that module.

module: htgt-dbconnect-trunk

t/01-dbconnect.t all tests pass
t/30-dbfactory.t all tests pass - but skipped tests that require loading of HTGTDB model 


Now, can go back to continue testing of htgtdb-trunk...

Created a directory to hold all the local htgt created modules. Then created soft links in that directory
to the checkouts in svn-checkout. This will be a concise and bounded directory of all the required local
HTGT modules.

export PERL5LIB=~/work/htgt_migration/htgt_lib:$PERL5LIB


SETUP - source  $HTGT_MIGRATION/setup_shell to set the environment correctly for this installation of perl and its modules.

Also, need a script or makefile to create symlinks in a $HTGT_HOME directory, which is where all the
modules of the local HTGT system will be installed.

The first attemp is:

$HTGT_MIGRATION/create_symlinks
